### 2016-06-29 GPCE2016/sections/RelatedWork.tex
paragraph on generated setter/getters in RW.

\paragraph{Automatically generated Getters and Setters}
\bruno{Need to discuss automatic generation of setter and
  getters, and then discuss this text about injections. See reviews
  and reply.}
By declaring fields in Newspeak and other languages,
the programmers specifies field signatures and (critically) the intention of storing such information. 
Then the language generates getters and setters.
Once state is abstracted away, it is well known that state
access can be replaced with computation, but the type of the field stays the same.
% Our fluid approach to state is specular:
In our approach,
the intention of storing the information is not expressed by the programmer and set in stone, 
but can vary by inheritance: we generate the idea of the field
just starting from signatures of getters and setters.
In this case, we leverage on our fluid state to changing the underling type of the field,
 and our \Q@with@ provides the right injection from the old type to the new.

>>>>

\paragraph{Automatic generation of getters and setters}
% \bruno{Need to discuss automatic generation of setter and
%   getters, and then discuss this text about injections. See reviews
%   and reply.}
is an old idea used in languages such as 
Self~\cite{Ungar1987self}, Dart~\cite{Dart} and Newspeak~\cite{Bracha_thenewspeak}.
% By declaring fields in Newspeak and other languages,
The programmers specifies field signatures and (critically) the intention of storing such information,  
then the language generates getters and setters.
Once state is abstracted away, it is well known that state
access can be replaced with computation, but the type of the field stays the same.
We do the opposite, the idea of the field is generated starting from signatures of 
getters and setters. % Our fluid approach to state is specular:
In our approach, the intention of storing the information is not expressed by the programmer and set in stone  
but can vary by inheritance. 
In this case, the underling type of the field can be changed by our fluid state, 
 and \Q@with@ methods provide the right injection from the old type to the new.
